---
title: "What makes a song hit top 100 on Spotify?"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Installing necessary packages:
```{r}
library(dplyr)
library(ggplot2)
library(CARS)
```

Summarize the data to see what variables we are working with:
```{r}
spotify_data <- read.csv("~/Desktop/projects/stats_projects/spotify_top100/top2018.csv")
summary(spotify_data)
```



Determine which artists have more than 1 song on the top 100 songs list:

```{r}
artists <- spotify_data$artists
n_occur <- data.frame(table(artists))
top_artists <- n_occur[n_occur$Freq > 1,]

ggplot(top_artists,aes(x=top_artists$artists,y=top_artists$Freq,label=top_artists$artists)) + geom_bar(stat="identity",fill="tomato2",width=0.5) + geom_text(aes(label=top_artists$Freq),color='white',hjust=2,size=3) +
coord_flip() +
labs(x='Number of Songs on Top 100 Chart',y='Artist',title='Artists with More than 1 Song on the Top 100 Chart') +
theme(plot.title=element_text(face='bold',size=15),axis.title=element_text(face='bold',size=10))
```

Exploring the correlation between "danceability" with different variables of the top 100 songs:
(insert spotify's definition of song factors)

```{r}
dance <- spotify_data$danceability
energy <- spotify_data$energy
loudness <- spotify_data$loudness
speech <- spotify_data$speechiness
acoustics <- spotify_data$acousticness
liveliness <- spotify_data$liveness
valence <- spotify_data$valence
tempo <- spotify_data$tempo
duration <- spotify_data$duration_ms
```

Build an initial model based on our intuition about "danceability":
```{r}
# Guess: danceability is correlated to liveliness, tempo, energy, and speechiness
model01 <- lm(dance ~ liveliness + tempo + energy + speech)
summary(model01)
```
```{r}
pairs(dance ~ liveliness + tempo + energy + speech)
```
(analysis of AVplots + pair plots)

It appears that liveliness, energy, and speech are weakly correlated to the "danceability" of a song. 

```{r}
model02 <- lm(dance~tempo+speech)
summary(model02)
```

